Data for the Ontario Restaurant Closures Experiment

### 2021-02-19 outputs/paper/data_simulation.Rmd
graphs, tables, and cross-referencing

## Survey 1
```{r, warning = FALSE}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(disability = sample(c("yes", "no"),
                             size = num_total,
                             prob = c(0.005, .995),
                             replace = TRUE))

@@

## Survey 2
```{r, warning = FALSE}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(disability = sample(c("yes", "no"),
                             size = num_total,
                             prob = c(0.005, .995),
                             replace = TRUE))

@@

set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
  filter(nonresponse != "no")

set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(which_partial = sample(c(4:num_cols_1), size = first(count(survey_1)), replace = TRUE))

@@

set.seed(19894)
survey_2 <- survey_2 %>%
  mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
  filter(nonresponse != "no")

set.seed(19894)
survey_2 <- survey_2 %>%
  mutate(which_partial = sample(c(4:num_cols_1), size = first(count(survey_2)), replace = TRUE))

>>>>

## Survey 1
```{r, warning = FALSE}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(disability = sample(c("yes", "no", "nonanswer"),
                             size = num_total,
                             prob = c(0.005, .985, 0.01),
                             replace = TRUE))

@@

## Survey 2
```{r, warning = FALSE}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(disability = sample(c("yes", "no", "nonanswer"),
                             size = num_total,
                             prob = c(0.005, .985, 0.01),
                             replace = TRUE))

@@

set.seed(19894)
survey_1 <- survey_1 %>%
  mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
  filter(nonresponse != "no")

set.seed(19894)
survey_1 <- survey_1 %>%
  mutate(which_partial = sample(c(4:num_cols_1), size = first(count(survey_1)), replace = TRUE))

@@

set.seed(19895)
survey_2 <- survey_2 %>%
  mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
  filter(nonresponse != "no")

set.seed(19895)
survey_2 <- survey_2 %>%
  mutate(which_partial = sample(c(4:num_cols_1), size = first(count(survey_2)), replace = TRUE))
